% Cover letter using letter.sty
\documentclass[10pt]{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-0.5in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{NAASC Postdoctoral Fellow \\
Charlottesville, VA, USA \\
}

\begin{flushleft}
{\large\bf Eamon O'Gorman - Cover Letter}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill School of Physics \\
\hfill Trinity College Dublin \\
\hfill Dublin 2 \\
\hfill Ireland \\
\hfill +353 (0)85 720 3415 \\
\hfill eogorma@tcd.ie \\

\end{flushright} 
\vfill % forces letterhead to top of page

\opening{To whom it may concern:} 

 
\noindent I am currently in the final stages of completing a Ph.D. in astrophysics at Trinity College Dublin, Ireland, under the supervision of Prof. Graham Harper. On September 30, 2013, I submitted my thesis (Title: \textit{Radio Interferometric Studies of Cool Evolved Stellar Winds}), and I successfully defended my thesis on November 15, 2013. I am due to graduate from Trinity College Dublin in April 2014 and envisage to continue with my research in stellar astrophysics thereafter. I can assure you that my technical experience in radio interferometry, scientific knowledge, and communication skills, make me a strong candidate for the NAASC postdoctoral fellowship.

\noindent My Ph.D. research has focused on understanding the atmospheres of red giants and red supergiants through multi-wavelength radio interferometric studies (both continuum and line emission). These stars have substantial mass-loss rates, but the mechanisms which heat and launch their outflows remain an enduring mystery. Progress in this field continues to be driven by observations, and this NAASC postdoctoral fellowship at Charlottesville would enable me to pursue such observations. 

\noindent I have extensive experience in reducing interferometric data at both millimeter and centimeter wavelengths, all of which have been carried out within CASA. During my Ph.D., I have been a successful P.I. on proposals to use the Combined Array for Research in Millimeter-wave Astronomy (CARMA) array, the Karl G. Jansky Very Large Array (VLA), and the Giant Metrewave Radio Telescope (GMRT). I have designed and planned all such observations and therefore have intensive experience in creating observing scripts and using online submission tools. I also have a keen interest in public outreach and would love to continue this interest into my postdoctoral career.

Thank you for taking the time to consider my credentials and I look forward to hearing from you.

Eamon O'Gorman
\\
\\
\\
\\
\\
\\
\\
\\
\end{letter}
 

\end{document}






