% Cover letter using letter.sty

\documentclass[11pt]{letter} % Uses 10pt
\usepackage{float}
\usepackage{caption}
\captionsetup{labelsep=space}

%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1.2in    % Make letterhead start about 1 inch from top of page 
\textheight=14in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\textheight 255mm


\begin{document}\pagenumbering{gobble}




\begin{flushleft}
{\large\bf Eamon O'Gorman - Bibliography}
\end{flushleft}
\hrule height 1pt
\begin{flushright}


\end{flushright} 
\vspace{1mm}

{\large
    \section{\mysidestyle \textbf{Refereed Publications}}}

{\normalsize
\vspace{3mm}
    \textbf{O'Gorman, E.}, Harper, G. M., Brown, A., Drake, S., Richards, A. M. S.
    \textsl{Multi-wavelength Radio Continuum Emission Studies of Dust-free Red Giants},
    2013, AJ, 146, 98.

\vspace{0mm}
    Richards, A. M. S., Davis, R. J., Decin, L., Etoka, S., Harper, G. M., Lim, J. J., Garrington, S. T., Gray, 	M. D., McDonald, I., \textbf{O'Gorman, E.}, Wittkowski, M.
    \textsl{e-MERLIN resolves Betelgeuse at $\lambda$ 5\,cm: hotspots at $5\,R_{\star}$},
    2013, MNRAS, 432, L61.

\vspace{0mm}
	\textbf{O'Gorman, E.}, Harper, G. M., Brown, J. M., Brown, A., Redfield, S., Richter, M. J., Requena-			Torres, M. A.
    \textsl{CARMA CO($J = 2-1$) Observations of the Circumstellar Envelope of Betelgeuse},
    2012, AJ, 144, 36.

\vspace{0mm}
	Sada, P. V., Deming, D., Jennings, D. E., Jackson, B. K., Hamilton, C. M., Fraine, J., Peterson, S. W., 		Haase, F., Bays, K., Lunsford, A., \textbf{O'Gorman, E.}
    \textsl{Extrasolar Planet Transits Observed at Kitt Peak National Observatory},
    2012, PASP, 124, 212.

\vspace{0mm}
	Sada, P. V., Deming, D., Jackson, B., Jennings, D. E., Peterson, S. W., Haase, F., Bays, K., \textbf{O'Gorman, E.}, Lundsford, A.
    \textsl{Recent Transits of the Super-Earth Exoplanet GJ 1214b},
    2010, ApJ, 720, L215.
}

\end{flushright} 
\vspace{6mm}

{\large
    \section{\mysidestyle \textbf{Non-refereed Publications}}}

{\normalsize
\vspace{3mm}
\textbf{O'Gorman, E.}, \& Harper, G. M., \textsl{What is Heating Arcturus' Wind?}, 2011, Proceedings of the 16th Cambridge Workshop on Cool Stars, Stellar Systems and the Sun. Astronomical Society of the Pacific Conference Series, 448, 691.
}

\end{flushright}
\end{document}






